---
title: "Exercise: Model Averaging and GitHub"
author: "Your Name"
date: "11/04/2021"
output:
  github_document:
    toc: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

Instructions:

1. Update the `author` field to your name(s) in line 3.

2. Run the following code and fill in the blanks. You may need to install the `mlmRev` package, but other than that you shouldn't need to change any R code below.

```{r load-pkgs, message = FALSE}
library(tidyverse)
library(mlmRev)  # if error, install the mlmRev package first:
# install.packages("mlmRev")
library(here)
library(haven)
library(lme4)
library(MuMIn)  # for model averaging
library(modelsummary)
theme_set(theme_bw())  # Theme; just my personal preference
```

## Import and Scale the Data

```{r import_sav, message = FALSE}
# Import HSB data from the mlmRev package
data(Hsb82, package = "mlmRev")
# Rename to hsball
hsball <- Hsb82
```

## Obtain a Subset of 50 Schools (~ 2,000 students)

```{r hsbsub}
# Create a subset of 50 schools
set.seed(2)  # make the results reproducible
random_schools <- sample(unique(hsball$school), size = 50)
hsbsub <- hsball %>% 
  filter(school %in% random_schools) %>% 
  # cluster-mean centeringn
  group_by(school) %>% 
  mutate(ses_cm = mean(ses),  # mean SES
         sx_cm = mean(sx == "Female"),  # proportion female
         minrty_cm = mean(minrty == "Yes"),  # proportion minority
         ses_cmc = ses - ses_cm) %>% 
  ungroup()
```

## Fit Four Separate Models

```{r m1-m3}
m1 <- lmer(mAch ~ sector * ses_cmc +
             (1 + ses_cmc | school), data = hsbsub, 
           na.action = "na.fail",  # needed for the `MuMIn` package
           REML = FALSE)  # use ML to get AIC/BIC
m2 <- lmer(mAch ~ ses_cmc + ses_cm + (1 + ses_cmc | school), data = hsbsub,
           na.action = "na.fail",  # needed for the `MuMIn` package
           REML = FALSE)  # use ML to get AIC/BIC
m3 <- lmer(mAch ~ minrty_cm + minrty + ses_cm + ses_cmc +
             (1 + minrty + ses_cmc | school), data = hsbsub, 
           na.action = "na.fail",  # needed for the `MuMIn` package
           REML = FALSE)  # use ML to get AIC/BIC
m4 <- lmer(mAch ~ (minrty_cm + minrty) * (ses_cm + ses_cmc) +
             (1 + minrty + ses_cmc | school), data = hsbsub, 
           na.action = "na.fail",  # needed for the `MuMIn` package
           REML = FALSE)  # use ML to get AIC/BIC
AIC(m1, m2, m3, m4)  # marginal AIC
```

Fill in the blank: Model ____ appears to have the best out-of-sample prediction accuracy?

## Averaging M1, M2, M3, and M4

In model averaging, the Akaike weights are usually used, defined as
$$\frac{\exp(-0.5 \times \Delta_m)}{\sum_i \exp(-0.5 \times \Delta_i)}, $$
where $\Delta_m = \text{AIC}_m - \text{AIC}_\text{min}$ is the difference between the AIC of model $m$ from the minimum AIC among all the candidate models. You can get the model weights with

```{r}
model.sel(m1, m2, m3, m4, rank = "AIC")  # see the last column
```

Fill in the blank: Model ____ has the highest weight

To average the models, we use

```{r m_avg1}
# Averaging
m_avg1 <- model.avg(m1, m2, m3, m4, rank = "AIC")
summary(m_avg1)
```

Now let's look at the prediction accuracy on the hold-out sample (i.e., the remaining 110 schools). 

### Test error

```{r}
# Validation sample
hsbtest <- hsball %>% 
  filter(!school %in% random_schools) %>% 
  # cluster-mean centeringn
  group_by(school) %>% 
  mutate(ses_cm = mean(ses),  # mean SES
         sx_cm = mean(sx == "Female"),  # proportion female
         minrty_cm = mean(minrty == "Yes"),  # proportion minority
         ses_cmc = ses - ses_cm) %>% 
  ungroup()
mse <- lapply(list(m1 = m1, m2 = m2, m3 = m3, m4 = m4, `m_avg1` = m_avg1), 
              function(m) {
                mean(
                  (predict(m, newdata = hsbtest, re.form = NA) -
                     hsbtest$mAch)^2
                )
              })
# Mean squared errors
unlist(mse)
```

Fill in the blank: From the output above, model ____ shows the highest out-of-sample prediction accuracy.

## Model Averaging of More Models

The following performs model averaging of 23 best possible submodels that contain `ses_cmc` and `ses_cm` out of the 7 predictors, using Akaike weights.

```{r m_full}
m_full <- lmer(mAch ~ ses_cmc + ses_cm +
                 minrty + minrty_cm + sx + sx_cm +
                 (1 + ses_cmc + minrty + sx | school), data = hsbsub, 
               na.action = "na.fail",
               REML = FALSE)
dd <- dredge(m_full, fixed = ~ ses_cmc + ses_cm, rank = "AIC")
# Average models with 95% of the Akaike weights
dd_models <- get.models(dd, subset = cumsum(weight) <= .95)
m_avg2 <- model.avg(dd_models)
summary(m_avg2)
# Mean squared error 
mean(
  (predict(m_avg2, newdata = hsbtest, re.form = NA) - hsbtest$mAch)^2
)
```

Note the above performs better than previous models.

The following shows the variance importance of the predictors. It adds up the weights of the models that contain a given predictor, for each predictor. 

```{r imp-avg2}
importance(m_avg2)
```

Fill in the blanks: Aside from `ses_cm` and `ses_cmc`, ______ are the most important for predicting `mAch`, while _____ is the least important?

To learn more about averaging, check out this paper: https://www.sciencedirect.com/science/article/pii/S0022249699912786
